\pkg{Rgbp}: An R Package for Gaussian, Poisson, and Binomial Hierarchical Modeling

### 2013-09-03 jss/article.tex
Tak edit on 3 Sep

The following code provides 31 RB unbiased coverage estimates for each hospital.
\begin{CodeChunk}
\begin{CodeInput}
R> pcv$coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.955 0.955 0.955 0.955 0.955 0.955 0.955 0.955 0.955 0.954 0.954 0.955 
[13] 0.954 0.955 0.954 0.954 0.954 0.955 0.954 0.954 0.954 0.954 0.954 0.954 
[25] 0.953 0.954 0.953 0.953 0.954 0.952 0.952
\end{CodeOutput}
\end{CodeChunk}

And the code below calculates 31 simple unbiased coverage estimates for each hospital.
\begin{CodeChunk}
\begin{CodeInput}
R> pcv$coverageS
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.960 0.953 0.956 0.952 0.957 0.957 0.960 0.949 0.949 0.944 0.951 0.947 
[13] 0.949 0.958 0.958 0.959 0.953 0.954 0.953 0.955 0.956 0.952 0.953 0.959 
[25] 0.945 0.945 0.953 0.946 0.953 0.948 0.955
\end{CodeOutput}
\end{CodeChunk}

The function \code{coverage} also calculates the standard errors for each hospital's RB unbiased coverage estimate defined as the square root of $S^{2}_{RB, j}/N_{sim}$, where $S^{2}_{RB, j}$ is the sample variance of 1,000 RB unbiased coverage estimates for the $j$-th hospital. The following code provides 31 standard errors.
\begin{CodeChunk}
\begin{CodeInput}
R> pcv$se.coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.0016 0.0016 0.0014 0.0013 0.0013 0.0013 0.0013 0.0013 0.0013 0.0013 0.0012 
[12] 0.0012 0.0012 0.0011 0.0011 0.0011 0.0011 0.0011 0.0011 0.0011 0.0011 0.0010
[23] 0.0010 0.0010 0.0010 0.0009 0.0009 0.0008 0.0008 0.0007 0.0007
\end{CodeOutput}
\end{CodeChunk}
Similarly, 31 standard errors for each simple unbiased coverage estimate are
\begin{CodeChunk}
\begin{CodeInput}
R> pcv$se.coverageS
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.0062 0.0067 0.0065 0.0068 0.0064 0.0064 0.0062 0.0070 0.0070 0.0073 0.0068 
[12] 0.0071 0.0070 0.0063 0.0063 0.0063 0.0067 0.0066 0.0067 0.0066 0.0065 0.0068
[23] 0.0067 0.0063 0.0072 0.0072 0.0067 0.0072 0.0067 0.0070 0.0066
\end{CodeOutput}
\end{CodeChunk}

Taking the first hospital as an example, the variance estimate of RB unbiased coverage estimate is about 15 times smaller than that of simple one. It means that 1,000 RB unbiased coverage estimates are as precise as 15,000 simple unbiased coverage estimates in terms of estimating true coverage probability for the first hospital.

@@

In addition, Rao-Blackwellized (RB) unbiased coverage estimate and its standard error for each school can be gotten with the command below.
\begin{CodeChunk}
\begin{CodeInput}
R> gcv$coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.964 0.958 0.964 0.960 0.956 0.959 0.958 0.966
\end{CodeOutput}
\end{CodeChunk}
\begin{CodeChunk}
\begin{CodeInput}
R> gcv$se.coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.0014 0.0013 0.0016 0.0014 0.0014 0.0012 0.0012 0.0017
\end{CodeOutput}
\end{CodeChunk}

@@

The Rao-Blackwellized unbiased coverage estimates and their standard errors for each player follow.
\begin{CodeChunk}
\begin{CodeInput}
R> bcv$coverageRB
\end{CodeInput}
%$
\begin{CodeOutput}
 [1] 0.973 0.973 0.974 0.971 0.971 0.973 0.972 0.973 0.972 0.973 0.971 0.973 
[13] 0.971 0.972 0.974 0.972 0.972 0.973
\end{CodeOutput}
\end{CodeChunk}
\begin{CodeChunk}
\begin{CodeInput}
R> bcv$se.coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.0010 0.0011 0.0011 0.0013 0.0012 0.0011 0.0012 0.0011 0.0012 0.0010 
[11] 0.0013 0.0012 0.0013 0.0013 0.0010 0.0010 0.0010 0.0010
\end{CodeOutput}
\end{CodeChunk}

>>>>

The following code provides 31 RB unbiased coverage estimates for each hospital.
\begin{CodeChunk}
\begin{CodeInput}
R> pcv$coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.956 0.956 0.956 0.955 0.955 0.955 0.955 0.955 0.955 0.955 0.955 0.954 
[13] 0.955 0.954 0.954 0.954 0.954 0.954 0.955 0.954 0.954 0.953 0.953 0.953
[25] 0.954 0.954 0.954 0.953 0.953 0.953 0.952
\end{CodeOutput}
\end{CodeChunk}

And the code below calculates 31 simple unbiased coverage estimates for each hospital.
\begin{CodeChunk}
\begin{CodeInput}
R> pcv$coverageS
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.947 0.952 0.963 0.961 0.957 0.957 0.959 0.952 0.957 0.957 0.941 0.958 
[13] 0.954 0.962 0.935 0.940 0.955 0.952 0.951 0.941 0.955 0.952 0.954 0.946 
[25] 0.942 0.952 0.958 0.945 0.938 0.958 0.948
\end{CodeOutput}
\end{CodeChunk}

The function \code{coverage} also calculates the standard errors for each hospital's RB unbiased coverage estimate defined as the square root of $S^{2}_{RB, j}/N_{sim}$, where $S^{2}_{RB, j}$ is the sample variance of 1,000 RB unbiased coverage estimates for the $j$-th hospital. The following code provides 31 standard errors.
\begin{CodeChunk}
\begin{CodeInput}
R> pcv$se.coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.0017 0.0017 0.0014 0.0014 0.0014 0.0014 0.0014 0.0014 0.0013 0.0013 0.0013 
[12] 0.0013 0.0012 0.0012 0.0012 0.0012 0.0011 0.0012 0.0011 0.0011 0.0011 0.0011
[23] 0.0010 0.0011 0.0010 0.0010 0.0009 0.0009 0.0009 0.0007 0.0007
\end{CodeOutput}
\end{CodeChunk}
Similarly, 31 standard errors for each simple unbiased coverage estimate are
\begin{CodeChunk}
\begin{CodeInput}
R> pcv$se.coverageS
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.0071 0.0068 0.0060 0.0061 0.0064 0.0064 0.0063 0.0068 0.0064 0.0064 0.0075 
[12] 0.0063 0.0066 0.0060 0.0078 0.0075 0.0066 0.0068 0.0068 0.0075 0.0066 0.0068 
[23] 0.0066 0.0072 0.0074 0.0068 0.0063 0.0072 0.0076 0.0063 0.0070
\end{CodeOutput}
\end{CodeChunk}

Taking the first hospital as an example, the variance estimate of RB unbiased coverage estimate is about 17 times smaller than that of simple one. It means that 1,000 RB unbiased coverage estimates are as precise as 17,000 simple unbiased coverage estimates in terms of estimating true coverage probability for the first hospital.

@@

In addition, Rao-Blackwellized (RB) unbiased coverage estimate and its standard error for each school can be gotten with the command below.
\begin{CodeChunk}
\begin{CodeInput}
R> gcv$coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.966 0.959 0.967 0.960 0.959 0.962 0.960 0.966
\end{CodeOutput}
\end{CodeChunk}
\begin{CodeChunk}
\begin{CodeInput}
R> gcv$se.coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.0013 0.0012 0.0013 0.0013 0.0011 0.0011 0.0010 0.0017
\end{CodeOutput}
\end{CodeChunk}

@@

The Rao-Blackwellized unbiased coverage estimates and their standard errors for each player follow.
\begin{CodeChunk}
\begin{CodeInput}
R> bcv$coverageRB
\end{CodeInput}
%$
\begin{CodeOutput}
 [1] 0.972 0.973 0.973 0.973 0.972 0.972 0.972 0.972 0.973 0.972 0.973 0.972 
[13] 0.973 0.973 0.971 0.973 0.971 0.973
\end{CodeOutput}
\end{CodeChunk}
\begin{CodeChunk}
\begin{CodeInput}
R> bcv$se.coverageRB
\end{CodeInput}
\begin{CodeOutput}
 [1] 0.0015 0.0011 0.0012 0.0011 0.0015 0.0012 0.0012 0.0010 0.0011 0.0012 
[11] 0.0010 0.0012 0.0010 0.0011 0.0013 0.0011 0.0013 0.0010
\end{CodeOutput}
\end{CodeChunk}
